---
title: "p8105_hw3_xl2934"
author: "Xiaoyang Li"
date: "2019/10/6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning  = FALSE)
library(tidyverse)
library(httr)
library(jsonlite)
```

# Problem 1
```{r}
# load data
library(p8105.datasets)
data("instacart")

str(instacart)
instacart
```

As the `str` function showing, `instacart` is a dataframe with 1384617 observations of  15 variables. There are some key variables.  `order_id` and `user_id` can help to make the dataframe more readable by using `pivot_wider`. `reordered` and variables about order time help us to analyse user's behavior. For example, we can conclude that ice cream is the most frequently ordered products late at night by counting observations with ice cream in specific time period.

* How many aisles are there, and which aisles are the most items ordered from.?
```{r}
aisle_count = instacart %>% 
  group_by(aisle) %>% 
  summarize(n = n()) 

aisle_count %>% 
  filter(min_rank(desc(n)) == 1) %>% 
  knitr::kable()
```
There are 134 aisles in total. Fresh vegetables are the most items ordered from.

* Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
aisle_count %>% 
  filter(n > 10000) %>% 
  arrange(n) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(
    title = "items' number ordered in aisles containing more than 10000 ordered",
    y = "number of item"
  )
# how to Arrange aisles sensibly  
```

* Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
  group_by(aisle, product_name) %>% 
  summarize(n = n()) %>% 
  filter(aisle == c("baking ingredients","dog food care","packaged vegetables fruits")  , min_rank(desc(n)) == 1) %>% 
  knitr::kable()
```

* Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table)
```{r}
instacart %>% 
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>% 
  summarize(
    mean_hour = mean(order_hour_of_day)
  ) %>% 
  pivot_wider(
    names_from = product_name,
    values_from = mean_hour
  ) %>% 
  knitr::kable(digits = 1)

# 2*7? order coffee ice cream and pink lady apples in the same time?
```


# Problem 2
```{r}
# data import

data("brfss_smart2010")

```
First, do some data cleaning:

* format the data to use appropriate variable names;
* focus on the “Overall Health” topic
* include only responses from “Excellent” to “Poor”
*organize responses as a factor taking levels ordered from “Poor” to “Excellent”
```{r}

# data cleanning
brfss_smart2010 = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response == c("Excellent", "Very good", "Good", "Fair", "Poor")) %>% 
  mutate(response = factor(response, levels = c("Poor","Fair", "Good","Very good","Excellent")))

```


Using this dataset, do or answer the following (commenting on the results of each):

* In 2002, which states were observed at 7 or more locations? What about in 2010?
```{r}
brfss_smart2010 %>% 
  filter(year == 2002) %>% 
  group_by(locationabbr) %>% 
  summarize(
    n_loc = n_distinct(locationdesc)
  ) %>% 
  filter(n_loc >= 7)

brfss_smart2010 %>% 
  filter(year == 2010) %>% 
  group_by(locationabbr) %>% 
  summarize(
    n_loc = n_distinct(locationdesc)
  ) %>% 
  filter(n_loc >= 7)
```
According to table(s), there is none states were observed at 7 or more locations in 2002. But there are 9 states were observed at 7 or more locations in 2010, containing CA, CO, FL, MA, MD, NE, NJ, NY, TX. 

* Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}
# build new dataset for plot
data_plot1 = 
  brfss_smart2010 %>% 
  filter(response == "Excellent") %>% 
  mutate(year = as.factor(year)) %>% 
  select(year, locationabbr, data_value) %>% 
  group_by(year, locationabbr) %>% 
  summarize(
    ave_value = mean(data_value)
  ) 

# make spaghetti plot
data_plot1 %>% 
  ggplot(aes( x = year, y = ave_value, group = locationabbr, color = locationabbr)) +
  geom_point() +
  geom_line()
  
```

* Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}
data_plot2 =
  brfss_smart2010 %>% 
  filter(year == c("2006", "2010"), locationabbr == "NY") %>% 
  select(year, response, data_value, locationdesc)

data_plot2 %>% 
  ggplot(aes(x = data_value, y = locationdesc, group = response, color = response)) +
  geom_point() +
  facet_grid(. ~ year)
```


# Problem 3

* Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
```{r}
# import data
data = read_csv(file = "./data/accel_data.csv")

# arrange day
day_of_week = tibble(day = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday",  "Sunday"), day_ = 1:7)

data = full_join(data, day_of_week) %>% 
  select(week, day_, everything()) 

# add variable about weekday and weekend
weekday = 
  data %>% 
  filter(day_ < 6) %>% 
  mutate(period = "weekday")

weekend = 
  data %>% 
  filter(day_ > 5) %>% 
  mutate(period = "weeekend")

data = bind_rows(weekday, weekend) %>% 
  select(period, everything()) %>% 
  arrange(week, day_) %>% 
  mutate(day_rank = 1:35)


# tidy and change the variable class
data = data  %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "time(min)",
    names_prefix = "activity.",
    values_to = "activity_count"
  )

# show the structure of data set
str(data)
```
The resulting data have 50400 observations in total and 8 variables including `period`, `week`, `day_`, `day_id`, `day`, `day_rank`, `time(min)` and `activity_count`.

* Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?
```{r}
total = 
  data %>% 
  group_by( week, day_rank, day) %>% 
  summarize(
    sum = sum(activity_count)
  )

total %>%
  knitr::kable()
 

```
```{r}
total %>% 
  ggplot(aes(x = day_rank, y = sum), fill = period) +
  geom_bar(stat = "identity")
```
It seems that the person have less activity on Monday of first two weeks and weekends of last two weeks. I don't think there are other trends apparent there.

* Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.
```{r fig.lenth = 50}
data
 data %>% 
  mutate(time_rank = 1:50400) %>% 
  ggplot(aes(x = time_rank, y = activity_count), color = period) +
  geom_bar(stat = "identity") +
  ylim(0,9000) +
  coord_flip()
```



